Preliminary test on OpenCV feature implementations

### 2013-03-13 text/opencv-test.tex
Added some youtube links to report

An alternative approach would be to sample characteristics from the face-patch 
in the form of feature points and compare how well these samples match feature 
points from other face-patches. If we can descripe the feature points in a 
light and affine transformation agnostic way, ideally we would be able to match 
them to corresponding feature points on other face-patches.

@@

\subsection{Theoretical shenanigans}

@@

I see two ways to possibly approach the problem. One is to find a mathematical 
method like sub-tree matching or similar approaches to match the two sets of 
feature points against each other for each image\footnote{I would be interested 
in hearing your input on this subject, or be put in contact with someone who 
might answer it}. A different (and in my opinion promising) approach is to 
forego the matching of two images entirely:

@@

>>>>

An alternative approach would be to sample characteristics from the face-patch 
in the form of feature points and compare how well these samples match feature 
points from other face-patches. If we can describe the feature points in a 
light and affine transformation agnostic way, ideally we would be able to match 
them to corresponding feature points on other face-patches.

@@

\subsection{Theoretical shenanigans\footnote{%
\href{http://www.youtube.com/watch?v=MFZG8KQJni8}{Relevant YouTube Clip}}}

@@

I see two ways to possibly approach the problem. One is to find a mathematical 
method like sub-tree matching or similar approaches to match the two sets of 
feature points against each other for each image\footnote{I would be interested 
in hearing your input on this subject}.  A different (and in my opinion 
promising) approach is to forego the matching of two images entirely:

@@

\subsection{Practical considerations}

The success of this approach is dependent on feature points being able to 
describe image keypoints in a light and affine transformation agnostic way. In 
the paper using an alignment free approach to match images I mentioned 
before\footnote{\cite{liao2011}} they whip up their own feature descriptor, an 
approach I'm not personally very convinced of since they never show their own 
descriptor to be superior to anything else than sift. Given that many new 
feature descriptors have come out in recent years, it seems to me much more 
sensible to use an already tested and confirmed approach than to cook up a new 
method, before I can show that coming up with a new feature descriptor is the 
only way to solve the problem\footnote{And in this case I'll most likely spend 
my thesis trying to come up with a feature descriptor instead of solving the 
original problem}.

Fortunately OpenCV implements a range of feature descriptors\footnote{To be 
precise they include an interface for: SIFT, SURF, ORB, BRISK, BRIEF and FREAK.  
I have however not been able to get FREAK to work}. So in order to see if any 
of these feature detectors might be usable and if yes, which ones, I decided to 
put them to the test.

\section{Getting some data\footnote{%
\href{http://www.youtube.com/watch?v=FQ3UrLQP2ok}{Relevant YouTube clip}}}
